quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-11 paper-quollr.Rmd
Trying to chnage the width

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "380px")

@@

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 450px; width: 200px; text-align: left;', htmltools::h5("a"), hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 450px; width: 200px; text-align: left;', htmltools::h5("b"), hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 400px; width: 200px;  text-align: left;', htmltools::h5("c"), wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 400px; width: 450px; text-align: left;', htmltools::div(
    style = "margin-left: 120px;",
    htmltools::h5("d"),
    scurve_umap_model_vis_n
  ))
    )
  ),
  device = "xs"
)

>>>>

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from_reindexed,
                         lineTo = tr_from_to_df_scurve$to_reindexed,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "400px", height = "450px")

@@

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 450px; width: 200px; text-align: left;', htmltools::h5("a"), hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 450px; width: 200px; text-align: left;', htmltools::h5("b"), hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 400px; width: 200px;  text-align: left;', htmltools::h5("c"), wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 600px; width: 450px; text-align: left;', htmltools::div(
    style = "margin-left: 120px; margin-top: 50px;",
    htmltools::h5("d"),
    scurve_umap_model_vis_n
  ))
    )
  ),
  device = "xs"
)
